Calculating life expectancy and exploring missingness

### 2016-10-25 Code/1_Explore_Data_v2.Rmd
still error checking this

>>>>

test1 <- cause_of_death_decomp(life.table1 = as.data.frame(list.life.tables[[black.index]]), 
                                                 life.table2 = as.data.frame(list.life.tables[[white.index]]), 
                                                 decomp.table = as.data.frame(list.age.decomp.tables[[i]]),
                                                 cod.table = ct.both, "Age2", "COD2", "prop1", "prop2")

test2 <- cause_of_death_decomp(life.table2 = as.data.frame(list.life.tables[[black.index]]), 
                                                 life.table1 = as.data.frame(list.life.tables[[white.index]]), 
                                                 decomp.table = as.data.frame(list.age.decomp.tables[[i]]),
                                                 cod.table = ct.both, "Age2", "COD2", "prop1", "prop2")

age_contr1 <- test1 %>% ungroup() %>% group_by(Ages) %>% summarise(age_contribution = sum(C_xi))
sum(age_contr1$age_contribution)
age_contr2 <- test2 %>% ungroup() %>% group_by(Ages) %>% summarise(age_contribution = sum(C_xi))
sum(age_contr2$age_contribution)
```
